### 2021-07-16 doc/thesis/chapters/introduction.tex
add a new chapter

\section{Goals}

The main goal of this thesis is to elaborate a system design for an embedded system, that combines all the knowledge of different disciplines and topics which are accumulated over the time of the university program, in a single project.

@@

%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%
%
%Thesis Design Decisions: \\
%\\
%Main focus on system design. \\
%\\
%How to achieve the same result in 3 (4?) different levels of abstraction?
%
%\begin{enumerate}
%  \item GnuRadio (?)
%  \item Matlab/Python
%  \item HLS\\
%      Implementation targeting Xilinx' ZedBoard.\\
%      Optionally: \\
%      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
%  \item VHDL
%\end{enumerate}
%\vspace{.5 cm}
%
%Compare:
%- Implementation effort (difficulty)
%- Implementation time
%- Usefulness on Target Systems (uC, SoC, RasPi, etc)
%- others?

>>>>

\section{Objective}

The main objective of this thesis is to elaborate a system design for an embedded system, that combines all the knowledge of different disciplines and topics which are accumulated over the time of the university program, in a single project.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%Thesis Design Decisions: \\
%\\
%Main focus on system design. \\
%\\
%How to achieve the same result in 3 (4?) different levels of abstraction?
%
%\begin{enumerate}
%  \item GnuRadio (?)
%  \item Matlab/Python
%  \item HLS\\
%      Implementation targeting Xilinx' ZedBoard.\\
%      Optionally: \\
%      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
%  \item VHDL
%\end{enumerate}
%\vspace{.5 cm}
%
%Compare:
%- Implementation effort (difficulty)
%- Implementation time
%- Usefulness on Target Systems (uC, SoC, RasPi, etc)
%- others?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FEEDBACK, Meeting 07-16-2021
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%formatting:
%- absätze überall gleich (mit oder ohne leerzeile)
%references:
%- hauptsache überall gleich (Fig.2.3 oder Sec.7.1 oder Eq.3 oder Chpt.4)
%- literature refs at the beginning of a chapter/section
%  like "this chapter is based on [1][4][5]."
%  or at the end of the last sentence like "...the end of this sentence. [7]"
%
%Allgemeiner Teil / Theorie:
% zusätzliches kapitel:
%   system design ansätze
%   - from algo to VHDL (book: vom algorithmus zur hardware)
%   - matlab to VHDL
%   - systementwuf richtung test driven design
%   --> design space exploration
%
%
% ganze Arbeit aufhängen an:
%   main objective: fit all the aspects (algorithm, impl, testing) into
%                   a single project
%
%
%
%
